Copy number inference with InferCNV

### 2024-05-21 analyses/cell-type-ewings/exploratory_analysis/04-infercnv.Rmd
Apply suggestions from code review
Co-authored-by: Joshua Shapiro <josh.shapiro@ccdatalab.org>

png_files |> 
  # make sure png files exists
  purrr::map(\(file)
    stopifnot("Missing PNG file" = file.exists(file))
  )

@@

# don't include the normal cells that were provided as reference in scaling 
reference_cells_only <- all_cnv_df |> 
  dplyr::filter(stringr::str_detect(subcluster, "reference")) |> 
  dplyr::mutate(has_cnv = NA,
                z_scaled_cnv = NA)

unknown_cells_only <- all_cnv_df |>
  dplyr::filter(stringr::str_detect(subcluster, "unknown")) |> 
  # get total number of chromosomes with cnvs per cell and then scale that number 
  dplyr::mutate(has_cnv = rowSums(across(has_cnv_cols)),
                z_scaled_cnv = scale(has_cnv))

@@

```{r}
ggplot(cnv_df, aes(x = mean_proportion)) +
  geom_density() +
  theme_bw()
```
It looks like we could use a cutoff of 0.1 here to classify tumor/normal cells. 
Let's see how this matches up with the tumor/normal classifications we defined just using total CNVs.

>>>>

png_files |> 
  # make sure png files exists
  purrr::walk(\(file)
    stopifnot("Missing PNG file" = file.exists(file))
  )

@@

# don't include the normal cells that were provided as reference in scaling 
cnv_df <- all_cnv_df |>
  # get total number of chromosomes with cnvs per cell and then scale that number 
  dplyr::mutate(
    has_cnv = ifelse(
      stringr::str_detect(subcluster, "reference"), 
      NA_real_, 
      rowSums(across(has_cnv_cols))
    ),
    z_scaled_cnv = scale(has_cnv))

@@

```{r}
ggplot(cnv_df, aes(x = mean_proportion)) +
  geom_density() +
  theme_bw()
```

It looks like we could use a cutoff of 0.1 here to classify tumor/normal cells. 
Let's see how this matches up with the tumor/normal classifications we defined just using total CNVs.
